---
title: "Lab 11: Comparative Structure Analysis"
author: "Griffin Norwood"
format: html
toc: true
---

## Finishing Work From Class 10
Loading in analysis packages for the protein structure sets:
```{r}
#install.packages("bio3d")
#install.packages("NGLVieweR")

#install.packages("pak")
#pak::pak("bioboot/bio3dview")

#install.packages("BiocManager")
#BiocManager::install("msa")
```

We will analyze the ADK starting with a singe ADK database accession code: "1ake_A"
```{r}
library(bio3d)
id <- "1ake_A"
aa <- get.seq("1ake_A")
aa
```
Now we search the PDB database to find all related entries.
```{r}
blast <- blast.pdb(aa)
#blast
```
```{r}
attributes(blast)
```
```{r}
head(blast$hit.tbl)
```
Making a little summary figure of these results:

```{r}
hits <- plot(blast)
hits
```
Out "top hits" i.e. the most similar entries in the databse are:
```{r}
hits$pdb.id
```

Making a zip file of all these entries using this code:
```{r}
files <- get.pdb(hits$pdb.id, path="pdbs", split=TRUE, gzip=TRUE)
```

Align and supperpose all these structures
```{r}
pdbs <- pdbaln(files, fit = TRUE, exefile="msa")
```

Side note:
```{r}
library(bio3dview)
view.pdbs(pdbs)
```

This is better but still difficult to see what is similar and different in all these structures or indeed learn much about how this family works.

Let's try PCA:

```{r}
pc <- pca(pdbs)
plot(pc)
```

```{r}
plot(pc, pc.axes = 1:2)
```

```{r}
view.pca(pc)
```

Write out a PDB "trajectory" for mol-star
```{r}
mktrj(pc, file= "pca_results.pdb")
```

## Class 11: Structural Analysis

Jumping to Section 6!

## Section 6: Generating our own structure predictions

Here we read the results from Alphafold and try to interpret all the models and quality score metrics:

```{r}
library(bio3d)
pth <- "betterdimer_23119/"
pdb.files <- list.files(path=pth, full.names = TRUE, pattern= ".pdb")
```

Align and supperpose all these models
```{r}
#just checking that the files are in the correct spot
file.exists(pdb.files)
```

```{r}
pdbs <- pdbaln(pdb.files, fit = TRUE, exefile="msa")
```

```{r}
library(bio3dview)
view.pdbs(pdbs)
```

```{r}
plot(pdbs$b[1,], typ="l", ylim=c(0,100), ylab = "pLDDT score") +
lines(pdbs$b[2,], typ="l", col="green") +
lines(pdbs$b[3,], typ="l", col="red") +
lines(pdbs$b[4,], typ="l", col="yellow") +
lines(pdbs$b[5,], typ="l", col="blue")
```

## Custom analysis of resulting models

```{r}
results_dir <- "betterdimer_23119/" 
aln_file <- list.files(path=results_dir,
                       pattern=".a3m$",
                        full.names = TRUE)
aln_file
```

```{r}
library(jsonlite)

# Listing of all PAE JSON files
pae_files <- list.files(path=results_dir,
                        pattern=".*model.*\\.json",
                        full.names = TRUE)

pae1 <- read_json(pae_files[1],simplifyVector = TRUE)
pae5 <- read_json(pae_files[5],simplifyVector = TRUE)

attributes(pae1)

head(pae1$plddt)
```
```{r}
pae1$max_pae
```

```{r}
pae5$max_pae
```

```{r}
plot.dmat(pae1$pae, 
          xlab="Residue Position (i)",
          ylab="Residue Position (j)")
```

```{r}
plot.dmat(pae5$pae, 
          xlab="Residue Position (i)",
          ylab="Residue Position (j)",
          grid.col = "black",
          zlim=c(0,30))
```
```{r}
pdb <- read.pdb("1hsg")
```

## Residue Conservation from alignment file

```{r}
aln_file <- list.files(path=results_dir,
                       pattern=".a3m$",
                        full.names = TRUE)
aln_file
```

```{r}
aln <- read.fasta(aln_file[1], to.upper = TRUE)
```

```{r}
dim(aln$ali)
```

```{r}
sim <- conserv(aln)
plotb3(sim[1:99], sse=trim.pdb(pdb, chain="A"),
       ylab="Conservation Score")
```

Find the consensus sequence:
```{r}
con <- consensus(aln, cutoff = 0.9)
con$seq
```

