---
title: "Lab 12 Homework"
author: "Griffin Norwood"
date: "2025-05-14"
output: pdf_document
---

## question 13 

Reading the data file into R (I messed up here and did not realize I should have been reading this file in as a "read.table", I was using "read.csv" and spent the past 2 days trying to figure out how to get this working. I watched the video all the way through and saw my mistake. I feel silly!)

```{r}
orm <- read.table("rs8067378_ENSG00000172057.6.txt")
head(orm)
```
It worked, great! I've been having trouble with that recently. Time to determine the sample sizes for each genotype;

```{r}
table(orm$geno)
```
Ok, sweet that works! I remembered this from today's lab 13 (which is after, but it's still cool that I remember). Time for median;

```{r}
tapply(orm$exp, orm$geno, median)
```

## Question 14: Boxplot
```{r}
library(ggplot2)

ggplot(orm)+
  aes(geno, exp)+
  geom_boxplot()+
  labs(x= "Genotype", y= "Expression")+
  theme_bw()
```

I read that this does not need to be flashy, I am tired and have spent a long time just trying to open the file correctly! But this is cute none-the-less!

